Uncovering invariant harmonic structures and schemata in music \\ \small A Deep Learning approach with contrastive learning and inductive bias

### 2023-03-04 music analysis/MSA.tex
Updates from Overleaf

It can be computed by representing the audio signal as a spectrogram (or any other suitable representation) and then calculating the similarity between all pairs of time frames in the spectrogram.

>>>>

It can be computed by representing the audio signal as a spectrogram (or any other suitable representation such as CQT or a Mel-spectrogram) and then calculating the similarity between all pairs of time frames in the spectrogram.
